### 2010-04-06 docs/runtime_parameters/runtime_parameters.tex
add intro
changed "min_width" to "cluster_min_width".  The other use of min_width, corresponding to the minimum size a grid can be at the coarsest level of multigrid, remains unchanged.

@@

@@

\verb=  min_width  = &   The minimum size on a side for a grid created using make\_new\_grids.  &  16 \\

@@

\verb=  pmask_x  = &   indicates whether the problem domain periodic in the x-direction  &  .false. \\
\verb=  pmask_y  = &   indicates whether the problem domain periodic in the y-direction  &  .false. \\
\verb=  pmask_z  = &   indicates whether the problem domain periodic in the z-direction  &  .false. \\

@@

>>>>

\verb=  cluster_min_width  = &   The minimum size on a side for a grid created using make\_new\_grids.  &  16 \\

@@

\verb=  diag_buf_size  = &   number of timesteps to buffer diagnostic output information before writing (note: not implemented for all problems)  &  10 \\

@@

@@

@@

\verb=  restart_into_finer  = &   restart and add a level of refinement  &  .false. \\
